Scikit-learn: API design for machine learning

### 2013-06-18 paper.tex
copyedit

The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{pythoncode}
y_pred = clf.predict(X_test)
\end{pythoncode}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{pythoncode}
from sklearn.cluster import KMeans

@@

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as inputs arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in the case of classification, or the mean squared
error in the case of regression. Not however that, from an API point of view,
the only guideline is that the \texttt{score} method returns a numerical value
such that the higher the better. As such, some unsupervised learning estimators
also exposes a \texttt{score} function, computing for instance the likelihood of
the given data.

>>>>

The \textit{predictor} interface extends the notion of an estimator
by adding a \texttt{predict}
method that takes an array \texttt{X\_test} and produces
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{pythoncode}
y_pred = clf.predict(X_test)
\end{pythoncode}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{pythoncode}
from sklearn.cluster import KMeans

@@

Finally, predictors should also provide a \texttt{score} function to assess the
performance on some input data. In supervised learning estimators, this method
takes as inputs arrays \texttt{X\_test} and \texttt{y\_test} and typically
computes the coefficient of determination between \texttt{y\_test} and
\texttt{predict(X\_test)} in the case of classification, or the mean squared
error in the case of regression. Not however that, from an API point of view,
the only guideline is that the \texttt{score} method returns a value
that quantifies the quality of its predictions (the higher, the better).
Unsupervised learning estimators may also exposes a \texttt{score} function
to compute, for instance, the likelihood of the given data under its model.
